Gravitational wave sources in our Galactic backyard: LISA predictions for BH and NS binaries

### 2021-06-08 paper/tex/sections/methods.tex
lots of results updates, mainly fiducial dists

We assume that stars with helium core masses between $1.6$--$2.25 \unit{M_{\odot}}$ \citep{Hurley+2002} experience electron-capture supernovae \citep{Nomoto+1984, Nomoto+1987, Ivanova+2008}. We set all remnant masses to $1.26 \unit{M_{\odot}}$ in this case as an approximation of the solution to Equation 8 of \citet{Timmes+1996}. For these supernovae, we set $\sigma_{\rm rms}^{\rm 1D} = 30 \unit{km}{s^{-1}}$ as in \citet{Pfahl+2002} and \citet{Podsiadlowski+2004}.

We assume that stars that undergo case BB mass transfer \citep{Dewi+2002} experience extreme stripping which leads to an ultra-stripped supernova \citep{Tauris+2013, Tauris+2015}. For these supernovae we calculate the remnant mass using the \citet{Fryer+2012} prescription and use $\sigma_{\rm rms}^{\rm 1D} = 30 \unit{km}{s^{-1}}$ (as with electron-capture supernovae).

>>>>

We assume that stars with helium core masses between $1.6$--$2.25 \unit{M_{\odot}}$ \citep{Hurley+2002} experience electron-capture supernovae (ECSN) \citep{Nomoto+1984, Nomoto+1987, Ivanova+2008}. We set all remnant masses to $1.26 \unit{M_{\odot}}$ in this case as an approximation of the solution to Equation 8 of \citet{Timmes+1996}. For these supernovae, we set $\sigma_{\rm rms}^{\rm 1D} = 30 \unit{km}{s^{-1}}$ \citep[e.g.][]{Pfahl+2002, Podsiadlowski+2004}.

We assume that stars that undergo case BB mass transfer \citep{Dewi+2002} experience extreme stripping which leads to an ultra-stripped supernova \citep{Tauris+2013, Tauris+2015}. For these supernovae we calculate the remnant mass using the \citet{Fryer+2012} prescription and use $\sigma_{\rm rms}^{\rm 1D} = 30 \unit{km}{s^{-1}}$ (as with ECSN).

### 2021-06-08 paper/tex/sections/results.tex
mini results change
lots of results updates, mainly fiducial dists

\todo{Note that the numbers/errors are subject to change in this section once the larger high Z simulations are done (thank you Floor!)}

In this section we present our main results for the detectable LISA DCO population. We find that on average, for our fiducial model, a four year LISA mission will detect \confinv{34.4}{20.9}{46.6} BHBHs, \confinv{29.9}{20.1}{47.4} BHNSs and \confinv{7.7}{5.0}{10.3} NSNSs where the error bars represent the 90\% confidence interval. We first show the distribution of the sources on the sensitivity curve in Section~\ref{sec:dcos_on_sc}, before exploring the variations in the detection rate over different physics variations in Section~\ref{sec:detection_rate_analysis} and analysing the parameter distributions for detectable sources in the fiducial model in Section~\ref{sec:fiducial_distributions}.

@@

We illustrate the distribution of detectable DCOs on the sensitivity curve in Figure~\ref{fig:dcos_on_sc}. This shows that the detectable population of these massive DCOs is concentrated at comparatively lower frequencies than the LISA verification binaries (shown as stars in the top panel) and the more numerous WDWD population \citep[e.g.][]{Korol+2017}. This is expected since producing the same SNR as a BHBH, BHNS or NSNS with a relatively lower mass (circular) WDWD requires a higher frequency. This finding is in agreement with \citet{Sesana+2020} and as noted in that work, this could possibly be used to distinguish these more massive DCOs from WDWDs. There are several other notable features in these distributions and we plot grid lines of constant distance and inspiral time to help to explain the shape of the distribution.

The straight diagonal lines show where a binary at a fixed distance and with the average chirp mass (annotated in each panel) would lie on the sensitivity curve for different frequencies. We would therefore expect that if a population was entirely circular, it should be bounded approximately between the $0.1$--$30 \unit{kpc}$ lines (roughly the minimum and maximum distance to a source in the Milky Way). From inspection of the bottom panels with each individual DCO type we see that, though this is the true for a large fraction of the population, there is a distinct subpopulation of binaries that extend downwards around $2 \times 10^{-3} \unit{Hz}$. This offshoot is composed of eccentric binaries for which the circular distance contours do not apply. For instance, we plot the 90\% contour of only the circular sources in our sample over the density distribution in each of the bottom panels and it is clear that the circular subsample is bounded by the distance lines. We also plot a line of constant distance at $30 \unit{kpc}$ for an eccentric binary with $e = 0.97$ to show the differences for eccentric sources. We also note that the peak of the density distribution coincides with the centre of the Milky Way as expected, since binaries are most likely to be formed towards the centre of the Galaxy.

We also plot vertical lines that give the inspiral time for a circular binary with the average chirp mass (annotated in each panel). From these lines, it is clear why the density distribution decreases with increasing frequency, since high frequencies correspond to short inspiral times and thus DCOs will spend less time in these regimes. We also see that the tail of the high frequency sources is more numerous near to the Galactic centre than at short distances. This is simply because there are more sources in the galactic centre and so the chances of `catching' a binary at high frequency are better.

\begin{figure*}[tp]
    \centering
    \includegraphics[width=\textwidth]{2_dcos_on_sc.png}
    \caption{Density distribution of detectable DCOs plotted over the LISA sensitivity curve, where the panels correspond to \textbf{top:} combined density plot for all DCO types (BHBH, BHNS and NSNS) \textbf{bottom:} three panels with individual density distribution of different DCO types. In each panel, we plot the total signal of binaries at their dominant frequency $n f_{\rm orb}$, such that $n$ is the harmonic that produces the most relative gravitational wave luminosity ($n = 2$ for circular binaries). If the density of points is below our lowest contour (2\%) then we plot the points as scatter points, where their sizes corresponds to their STROOPWAFEL weights. The inset colourbars indicate the percentage of the population represented by each contour and the annotated mass is the average chirp mass for all binaries in the panel, which is used in plotting the grid lines. We plot diagonal lines of constant distance, where the straight lines show the signal for a circular binary of average chirp mass, whilst the curved line shows the signal for an eccentric binary with $e = 0.97$. The vertical lines indicate the inspiral time for a circular binary with the average chirp mass. In the top panel we overlay the LISA verification binaries from \citet{Kupfer+2018}. In the bottom panels we add the 90\% contour line for only the circular sources to show how the distribution changes without eccentric sources present.}
    \label{fig:dcos_on_sc}
\end{figure*}

\subsection{Detection rates}\label{sec:detection_rate_analysis}
We find that for our fiducial model, a four year LISA mission will detect \confinv{34.4}{20.9}{46.6} BHBHs, \confinv{29.9}{20.1}{47.4} BHNSs and \confinv{7.7}{5.0}{10.3} NSNSs, where the error bars represent the 90\% confidence interval. Increasing the LISA mission length to ten years changes the number of detections to \confinv{42.0}{17.3}{17.3}, \confinv{44.5}{17.8}{20.7} and \confinv{19.3}{8.0}{9.7} respectively. In Figure~\ref{fig:detection_rates}, we show the expected number of LISA detections for each model variation and discuss the prominent trends in the following sections. We show the rates and uncertainties plotted in this figure in Table~\ref{tab:detection_rates}.

\begin{figure*}[p]
    \centering
    \includegraphics[width=\textwidth]{3_dco_detections.pdf}
    \caption{The number of expected detections in the LISA mission for different DCO types and model variations. Error bars show the 50\% (solid) and 90\% (dotted) confidence intervals. The left axis and grid lines show the number of detections in a four year LISA mission and the right axis shows an approximation of the number of detections in a 10 year mission (we scale the axis by $\sqrt{T_{\rm obs}}$, see Table~\ref{tab:detection_rates} for exact rates). Each model is described in further detail in Table~\ref{tab:physics_variations} and details of the fiducial assumptions are in Section~\ref{sec:fiducial_physics}. \todo{@ALL, ignore models P and Q for now}}
    \label{fig:detection_rates}
\end{figure*}

@@

\todo{This section is not currently up to date, waiting for new sims before writing more}

@@

\subsubsection{Black Hole Mass}
For both the BHBHs and BHNSs, the black hole mass distribution extends across relatively low masses, with $83\%$ and $90\%$ respectively below $10 \unit{M_{\odot}}$. This is because, at the high metallicities in the Milky Way, stellar winds are much stronger and strip away much of the stellar mass before BH formation. The mass distribution also extends down to $2.5 \unit{M_{\odot}}$, our fiducial maximum neutron star mass, since the \citet{Fryer+2012} \textit{delayed} remnant mass prescription does not produce a mass gap between neutron stars and black holes. Thus BHBHs and BHNSs detected by LISA could be ideal for ascertaining whether there exists a lower mass gap between neutron stars and black holes.

The bimodality of the BHBH distribution is a result of most detectable BHBHs in our sample having unequal mass ratios. The two peaks are from the primary and secondary black hole masses and we show their individual distributions with the dotted curves.

The reasoning for these unequal mass ratio is as follows: in order to produce a BHBH, most formation channels require at least the first mass transfer to be stable. This stability is strongly dependent on the mass ratio such that equal mass ratios (at the moment of mass transfer) are preferred for creating BHBHs. Yet, since stellar winds are so strong at high metallicity, and even stronger for more massive stars, the primary star will experience significant mass loss and so an initially \textit{unequal} mass ratio is preferred so that the masses are more balanced at the first instance of mass transfer. Since mass transfer occurs after the end of the main sequence for most of our BHBHs, the star will have a well defined core and these core masses, which go on to form BHs, will reflect the initially unequal mass ratios.

\subsubsection{Neutron Star Mass}
The neutron star mass distribution shows that most neutron stars have low masses, with $69\%$ and $87\%$ having masses below $1.5 \unit{M_{\odot}}$ for BHNSs and NSNSs respectively. The lacks of neutron stars around $1.7 \unit{M_{\odot}}$ and the subsequent small peaks are artifacts of the discontinuous nature of the \citet{Fryer+2012} remnant mass prescription.

\subsubsection{Eccentricity}
The eccentricity distributions show that detectable BHBHs are the most eccentric of the three DCOs. This may seem counter-intuitive since neutron stars receive stronger natal kicks, which cause the orbit to become eccentric. However, these stronger kicks often instead result in disrupted or too-wide binaries. In contrast, BHBHs can receive strong kicks that impart high eccentricity without disrupting and thus tend to be more eccentric. This effect is compounded by the fact that we can see BHBHs at lower orbital frequencies, meaning that they have not had as much time to circularise and so still have significant eccentricity by the time of the LISA mission.

\subsubsection{Orbital Frequency and Frequency Evolution}
The orbital frequency distributions for BHBHs, BHNSs and NSNSs peak at increasing frequencies. This is because a higher mass DCO at the same distance and eccentricity requires a lower frequency to produce the same signal-to-noise ratio and thus be detected. The BHBH distribution also has a tail that extends to $4 \times 10^{-6} \unit{Hz}$, which is comprised of highly eccentric binaries since eccentricity moves the dominant harmonic to higher frequencies. Similar tails are not as prevalent for BHNSs and NSNSs as they do not have as many eccentric binaries.

\subsubsection{Luminosity Distance}
Each DCO's luminosity distance distribution peaks around $8 \unit{kpc}$ since this is the distance to the centre of the Milky Way and thus the most dense location of DCOs. Each DCO also has a shoulder at lower distances since closer binaries are easier to detect. This shoulder is more prominent for the NSNS distribution since their lower relative masses require a smaller distance in order to be detected on average.

\subsubsection{Inspiral Time}
Each DCO has a strong peak at small inspiral times since higher metallicities lead to tighter binaries and thus shorter inspiral times.

\begin{figure*}[htbp]
    \centering
    \includegraphics[width=\textwidth]{4_distribution_grid_4yr.pdf}
    \caption{Distributions for various parameters of the DCOs that are detectable in a 4 year LISA mission in our fiducial model. Each panel shows the distribution of a single parameter, where the colour denotes the DCO type. We also plot the 1- and 2-$\sigma$ uncertainties (obtained via bootstrapping) with the dark and light shaded areas respectively. The first two rows (excluding metallicity) use kernel density estimators to show the distributions. The metallicity panel shows the distribution over the metallicity bins used in our population synthesis, which we show in the grid lines. The final three panels for the cumulative distribution functions for observables, normalised to the expected number of fiducial detections in a four year LISA mission. The dark shaded areas indicate regimes in which the quantity cannot be measured. The dotted lines in the angular resolution plot show the maximum angular resolution that can be covered by a single pointing of the labelled instrument. In Section~\ref{sec:fiducial_distributions} we discuss the features of the distributions.}
    \label{fig:fiducial_pdf_distributions}
\end{figure*}

\subsection{Model variations}

>>>>

In this section we present our main results for the detectable LISA DCO population. We find that, for our fiducial model, a four year LISA mission will detect \confinv{30.6}{20.5}{51.1} BHBHs, \confinv{26.4}{17.3}{48.5} BHNSs and \confinv{7.1}{4.8}{10.8} NSNSs where the error bars represent the 90\% confidence interval. We first show the distribution of the sources on the sensitivity curve in Section~\ref{sec:dcos_on_sc}, before exploring the variations in the detection rate over different physics variations in Section~\ref{sec:detection_rate_analysis} and analysing the parameter distributions for detectable sources in the fiducial model in Section~\ref{sec:fiducial_distributions}.

@@

We illustrate the distribution of detectable DCOs on the LISA sensitivity curve in Figure~\ref{fig:dcos_on_sc}. This shows that the detectable population of these massive DCOs is concentrated at comparatively lower frequencies than the LISA verification binaries (shown as stars in the top panel) and the more numerous WDWD population \citep[e.g.][]{Korol+2017}. This is expected since producing the same SNR as a BHBH, BHNS or NSNS with a relatively lower mass (circular) WDWD requires a higher frequency. This finding is in agreement with \citet{Sesana+2020} and as noted in that work, this could possibly be used to distinguish these more massive DCOs from WDWDs. There are several other notable features in these distributions and we plot grid lines of constant distance and inspiral time to help to explain the shape of the distribution.

The straight diagonal lines show where a binary at a fixed distance and with the average chirp mass (annotated in each panel) would lie on the sensitivity curve for different frequencies. We would therefore expect that if a population was entirely circular, it should be bounded approximately between the $0.1$--$30 \unit{kpc}$ lines (roughly the minimum and maximum distance to a source in the Milky Way). From inspection of the bottom panels with each individual DCO type we see that, though this is the true for a large fraction of the population, there is a distinct subpopulation of binaries that extend downwards, especially around $2 \unit{mHz}$. This offshoot is composed of eccentric binaries for which the circular distance contours do not apply. For instance, we plot the 90\% contour of only the circular sources in our sample over the density distribution in each of the bottom panels and it is clear that the circular subsample is bounded by the distance lines. We also plot a line of constant distance at $30 \unit{kpc}$ for an eccentric binary with $e = 0.98$ to show the differences for eccentric sources. Additionally, we note that the peak of the density distribution coincides with the centre of the Milky Way as expected, since binaries are most likely to be formed towards the centre of the Galaxy.

We plot vertical lines that give the inspiral time for a circular binary with the average chirp mass (annotated in each panel). From these lines we can understand the trend of the density distribution decreasing with increasing frequency. Sources with higher frequencies have shorter inspiral times and thus DCOs will spend less time in these regimes, meaning that more sources are detected at lower frequencies. Note that these inspiral time lines should only be used as guidelines for the population as a whole, as the inspiral time of each individual source will be a function of its mass and eccentricity. It is also evident for each DCO source that the tail of the high frequency sources is more numerous near to the Galactic centre than at short distances. This is simply because there are more sources in the galactic centre and so the chances of `catching' a binary at high frequency are better.

\begin{figure*}[tp]
    \centering
    \includegraphics[width=\textwidth]{2_dcos_on_sc.png}
    \caption{Density distribution of detectable DCOs plotted over the LISA sensitivity curve, where each panel corresponds to \textbf{top:} combined density plot for all DCO types (BHBH, BHNS and NSNS) \textbf{bottom:} three panels with individual density distribution of different DCO types. In each panel, we plot the total signal of binaries at their dominant frequency $n f_{\rm orb}$, such that $n$ is the harmonic that produces the most relative gravitational wave luminosity ($n = 2$ for circular binaries). If the density of points is below our lowest contour (2\%) then we plot the points as scatter points, where their sizes corresponds to their STROOPWAFEL weights. The inset colourbars indicate the percentage of the population represented by each contour and the annotated mass is the average chirp mass for all binaries in the panel, which is used in plotting the grid lines. We plot diagonal lines of constant distance, where the straight lines show the signal for a circular binary of average chirp mass, whilst the curved line shows the signal for an eccentric binary with $e = 0.98$. The vertical lines indicate the inspiral time for a circular binary with the average chirp mass. In the top panel we overlay the LISA verification binaries from \citet{Kupfer+2018}. In the bottom panels we add the 90\% contour line for only the circular sources to show how the distribution changes without eccentric sources present.}
    \label{fig:dcos_on_sc}
\end{figure*}

\subsection{Detection rates}\label{sec:detection_rate_analysis}
\todo{I will be updating this section once the other physics variations are done running. There will be a couple of new models and the current ones will have better high Z resolution.}
We find that for our fiducial model, a four year LISA mission will detect \confinv{30.6}{20.5}{51.1} BHBHs, \confinv{26.4}{17.3}{48.5} BHNSs and \confinv{7.1}{4.8}{10.8} NSNSs, where the error bars represent the 90\% confidence interval. Increasing the LISA mission length to ten years changes the number of detections to \confinv{50.6}{29.2}{63.3}, \confinv{46.2}{25.7}{99.3} and \confinv{12.1}{6.9}{13.5} respectively. In Figure~\ref{fig:detection_rates}, we show the expected number of LISA detections for each model variation and discuss the prominent trends in the following sections. We show the rates and uncertainties plotted in this figure in Table~\ref{tab:detection_rates}.

\begin{figure*}[p]
    \centering
    \includegraphics[width=\textwidth]{3_dco_detections.pdf}
    \caption{The number of expected detections in the LISA mission for different DCO types and model variations. Error bars show the 50\% (solid) and 90\% (dotted) confidence intervals. The left axis and grid lines show the number of detections in a four year LISA mission and the right axis shows an approximation of the number of detections in a 10 year mission (we scale the axis by $\sqrt{T_{\rm obs}}$, see Table~\ref{tab:detection_rates} for exact rates). Each model is described in further detail in Table~\ref{tab:physics_variations} and details of the fiducial assumptions are in Section~\ref{sec:fiducial_physics}. \todo{subject to change with the updated/new models}}
    \label{fig:detection_rates}
\end{figure*}

@@

@@

\begin{figure*}[htbp]
    \centering
    \includegraphics[width=\textwidth]{4_distribution_grid_4yr.pdf}
    \caption{Distributions for various parameters of the DCOs that are detectable in a 4 year LISA mission in our fiducial model. Each panel shows the distribution of a single parameter, where the colour denotes the DCO type. We also plot the 1- and 2-$\sigma$ uncertainties (obtained via bootstrapping) with the dark and light shaded areas respectively. The first two rows (excluding metallicity) use kernel density estimators to show the distributions. The dotted lines in the black hole mass panel show the individual distributions of the primary and secondary masses. The metallicity panel shows the distribution over the metallicity bins used in our population synthesis, which we show in the grid lines. The final three panels for the cumulative distribution functions for observables, normalised to the expected number of fiducial detections in a four year LISA mission. The dark shaded areas indicate regimes in which the quantity cannot be measured. The dotted lines in the angular resolution plot show the maximum angular resolution that can be covered by a single pointing of the labelled instrument. In Section~\ref{sec:fiducial_distributions} we discuss the features of the distributions.}
    \label{fig:fiducial_pdf_distributions}
\end{figure*}

\subsubsection{Black Hole Mass}
For both the BHBHs and BHNSs, the black hole mass distribution extends across relatively low masses, with $88\%$ and $90\%$ respectively below $11 \unit{M_{\odot}}$. This is because, at the high metallicities in the Milky Way, stellar winds are much stronger and strip away much of the stellar mass before BH formation. The mass distribution extends down to $2.5 \unit{M_{\odot}}$, our fiducial maximum neutron star mass, since the \citet{Fryer+2012} \textit{delayed} remnant mass prescription does not produce a mass gap between neutron stars and black holes. Indeed we expect $35\%$ and $39\%$ of detected BHBH and BHNS systems to contain a black hole in the lower mass gap. Therefore, LISA could help to confirm or rule out the existence of the lower mass gap.

The bimodality of the BHBH distribution is a result of most detectable BHBHs in our sample having unequal mass ratios. The two peaks are from the primary and secondary black hole masses, which peak around $8 \unit{M_{\odot}}$ and $3.5 \unit{M_{\odot}}$ respectively. We show these individual distributions as dotted curves below the main BHBH distribution.

The reasoning for these unequal mass ratio systems is as follows: in order to produce a BHBH, most formation channels require at least the first mass transfer to be stable. This stability is strongly dependent on the mass ratio such that equal mass ratios (at the moment of mass transfer) are preferred for creating BHBHs. Yet, since stellar winds are so strong at high metallicity, and even stronger for more massive stars, the primary star will experience significant mass loss and so an initially \textit{unequal} mass ratio is preferred so that the masses are more balanced at the first instance of mass transfer. Since mass transfer occurs after the end of the main sequence for most of our BHBHs, the star will have a well defined core and these core masses, which go on to form BHs, will reflect the initially unequal mass ratios.

\subsubsection{Neutron Star Mass}
The neutron star mass distribution shows that most neutron stars have low masses, with $77\%$ and $91\%$ having masses below $1.7 \unit{M_{\odot}}$ for BHNSs and NSNSs respectively. The lack of neutron stars around $1.7 \unit{M_{\odot}}$ and the subsequent small peaks are artifacts of the discontinuous nature of the \citet{Fryer+2012} remnant mass prescription and do not have strong effects since the vast majority of NSs are formed with lower masses.

Both distributions have notable peaks around $1.26 \unit{M_{\odot}}$, though more strongly in the NSNS case, which are a result of the combination of two effects. Firstly, we set the remnant mass for all electron-capture supernovae to $1.26 \unit{M_\odot}$ (see Sec.~\ref{sec:fiducial_physics}) and thus this leads to a pileup when many systems are formed through ECSN. In addition, the Fryer remnant mass prescription gives a fixed fallback mass for any star with a CO core mass less than $2.5 \unit{M_\odot}$, such that many NSs are given the identical mass of $1.278 \unit{M_\odot}$ in the \textit{delayed} prescription \citep[see][Eq.~19]{Fryer+2012}.

\subsubsection{Orbital Frequency}
The orbital frequency distributions for BHBHs, BHNSs and NSNSs peak at progressively increasing frequencies. This is because a higher mass DCO at the same distance and eccentricity requires a lower frequency to produce the same signal-to-noise ratio and thus be detected. The BHBH distribution has a tail that extends to $8 \times 10^{-6} \unit{Hz}$, which is comprised of highly eccentric binaries. These systems are still detectable by LISA as the high eccentricity means that the majority of the GW signal is emitted at higher harmonics at higher frequencies that are located in the LISA band. Similar tails are not as prevalent for BHNSs and NSNSs as they do not have as many eccentric binaries.

\subsubsection{Luminosity Distance}
Each DCO's luminosity distance distribution peaks around $8 \unit{kpc}$ since this is the distance to the centre of the Milky Way and thus the most dense location of DCOs. There is a clear bias in each distribution for systems at lower distances since closer binaries are easier to detect. This bias is most prominent for the NSNS distribution since, on average, their lower relative masses require a smaller distance in order to be detected.

\subsubsection{Lookback Time}
Although when creating each mock Milky Way galaxy the lookback time is drawn independently from other parameters, and in the same way for every DCO type, the distributions are clearly different for each type of DCO. This is because for a binary to be detectable, it must have an orbital frequency within the LISA band. Therefore a binary needs to have completed most of its inspiral to be visible in the LISA band and thus detectable systems will tend to have lookback time that are close to their merger times, which \textit{are} a function of other binary parameters.

Since most of the DCOs are formed through common envelope events, their initial separations are relatively tight and so if a binary it given a long lookback time, it will have merged before the LISA mission. This explains the peak in each distribution at short lookback times. The later lookback times correspond to systems that are formed through channels in which mass transfer is only stable and no common envelope event occurs.

The trends across the different DCO types can be explained by considering that the merger time is a function of the masses, frequency and eccentricity of th source. This dependence can be approximately written as $t_{\rm merge} \propto f_{\rm orb}^{-4} m_1^{-3} (1 - e^2)^{-7/2}$,  \citep[][Eq.~5.14]{Peters+1964}. Therefore, although NSNSs are the lowest mass systems, their relatively higher orbital frequencies means that they have the shortest merger times. This same logic implies that BHNSs should have the next shortest merger times and then BHBHs. This order is flipped due to the fact that high eccentricity results in a shorter merger time and we find that LISA detectable BHNSs are mostly circular, whilst BHBHs have a significant highly eccentric subpopulation.

\subsubsection{Metallicity}
\todo{Returning to this once I've made the plot that compares the Milky Way distribution and formation rates}

\subsubsection{Eccentricity}
The eccentricity distributions show that detectable BHBHs are the most eccentric of the three DCOs. This may seem counter-intuitive since neutron stars receive stronger natal kicks, which cause the orbit to become eccentric. However, these stronger kicks often instead result in disrupted or too-wide binaries in more weakly bound NSNSs. In contrast, BHBHs can receive strong kicks that impart high eccentricity without disrupting and thus tend to be more eccentric. This effect is compounded by the fact that we can see BHBHs at lower orbital frequencies, meaning that they have not had as much time to circularise and so still have significant eccentricity by the time of the LISA mission.

A significant fraction of DCOs in each population have eccentricities greater than 0.01, the lower bound on the measurable eccentricity with LISA proposed by \citet{Nishizawa+2016}, which we indicate with the shaded area. We discuss the estimation of the eccentricity uncertainty further in Section~\ref{sec:measurement_uncertainties}

\subsection{Measurement Uncertainties}\label{sec:measurement_uncertainties}
\todo{will fill with info on eccentricity, chirp mass and angular resolution uncertainties}

\subsection{Model variations}
\todo{This will be about how the shapes change with model variations}
